\section{Holographic Visualization}
\label{sec.holographic_visualization}

Holograms are expected to show visual effects of a 3D scene as a Volume Of Interest (VOI) projected outside the screen. The projection keep all the depth cues of the objects of the VOI: the relative sizes of the objects from the perspective deformation, the stereo depth perception from stereo convergence, binocular parallax and ocular accommodation of the eyes by focusing at different distances; the motion parallax~\cite{li2012} from the difference in the positions of the objects as the viewer moves, the monocular occlusion~\cite{Lucente1995} when one part of image is obstructed by another overlapping part; and pictorial monocular depth cues of texture gradient, aerial perspective, shading, and relative sizes~\cite{Lucente1995}. 

The hologram has an unique feature: viewers are allowed to walk around the VOI and have a \emph{surround viewing}~\cite{debevec2006}, a shared visualization in different angles that is naturally perceived by the eyes without any wearable apparatus. Additionally to that, two or more viewers can view the VOI in different angles because the viewing rays are propagated in a Field of View (FOV) from the holographic apparatus~\cite{Lucente1992}. The current CGH displays have a limited FOV of $60^{\circ}$~\cite{Slinger2005, Lucente1995} due the compromise of the quality of the hologram and computational processing power.

The surround viewing, combined with the depth cues, creates the illusion effect of Pepper's Ghost~\cite{smithwick2014}, which means that the viewer can interact with the VOI with no physical barriers. The practical applications for the combined 3D visualization and interaction can be illustrated, but not limited, in Medical Imaging. For example, a scene of 3D reconstructed organs from 3D medical imagery of 3D Computed Tomography (CT) scans or Magnetic Resonance Imaging (MRI) composes the VOI and is projected as a hologram. The organs are the objects that can be manipulated \emph{in locus} for virtual surgery, and there is no display screen acting as a physical barrier between the object and viewer. Any examination of the organs is provided by the surround viewing and depth cues of the VOI. The surgery simulation is achieved because the spectral illusion is created for the surgeon in a Virtual Reality (VR) environment.

\input{sec_holographic_emulation}
\input{sec_holographic_pipeline}

%\input{sec_holographic_projection}